Our peculiar motion across the Universe

### 2019-07-03 paper/main.tex
edit

\documentclass[onecolumn]{aastex62}
\submitjournal{ApJL}
\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

>>>>

\documentclass[onecolumn]{aastex62}
\submitjournal{ApJL}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc\ }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc\ }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc\ }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc\ }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\kms}{{\ifmmode{{\rm km\, {s}^{-1}}}\else{km s$^{-1}$}\fi}}

\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

\section{Numerical Setup}

We use simulations boxes from the Abacus project \cite{abacus}. 
Each box has a size of $L_{\rm box}=720$\hMpc and was simulated
with $1440^3$ particles and a resulting particle mass of $\sim 1\times
10^{10}$\hMpc.
Each box also have 41 different $\omega$CDM cosmological parameters
which are phase-matched to isolate cosmology dependences.
In our analysis we use the Friends-of-Friends (FOF) catalogs built on
the snapshot at redshift of $z=0.1$.

\section{Sample Selection}

We start by selecting all halos with a maximum circular velocity,
in the range $200\kms < v_{\rm max}< 250 \kms$ 
Then we proceed to use these halos to find what we call an Isolated Pair
(IP).
IPs are two halos, $A$ and $B$, that do not have any other third halo
with $v_{\rm max}>200$\kms closer than the pair separation.
We follow a convention where $A$ refers to the least massive halo in
the pair.

From this pair we measure the following quantities: the maximum
circular velocity for the two halos, peculiar velocities $\vec{v}_p$, 
separation vector $\vec{r}_{AB}$, tangential velocity of $B$ with
respect to $A$, $v_{t}$ and the radial velocity of $B$ with respect
to $B$ after taking into account Hubble expansion $v_r$.

From the IP sample we select the pairs with some similarity to the
observed LG. 
The conditions we impose are the following: the maximum
circular velocity should for both halos in the pair must be less than
$250$ \kms, the relative radial velocity should be negative and the
magnitude of the tangential velocity should be lower than the
magnitude of the radial velocity. 
We refer to this sample simply as the pair sample. 
Only about $1\%$ of the halos in the initial sample are found in
the pair sample. 
This is consistent with previous results that show that the fraction
of LG pairs in a cosmological context

\section{Results}

\section{Conclusions}
